Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Edits to Method and added references

The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
occurring between March 30, 2012 and June 15, 2012. Using the Twitter
streaming API, servers at the University of Texas at Austin collected
the tweets. The servers were run on a stable (LTS) version of Ubuntu
Linus, 10.04, and were connected directly to the high-bandwidth UT network
maintained by IT services.

Tweets collected contained one or more of the following keywords:
“syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These
keywords were chosen based on the most distinctive terms used in news
articles covering the Arab Spring in Syria at the time. A node.js script
was used to reinitialize the connection to Twitter's servers whenever the
script timed out due to a period of silence. The script requested data from
the API endpoint using basic HTTP authentication (OAuth was optional, at
the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored
the data directly to the local hard disk. The tweets were then post-processed
with a Python script to convert the JSON-formatted tweets to tab-separated
files and were then compressed to maximize storage efficiency.

@@

### Event Data
Event data were obtained from the 2012 Integrated Crisis Early Warning
System [ICEWS; @DVN/28075_2015]. The event data were first filtered to
remove incomplete and incorrectly formatted data. They were then filtered
to include only events that were directed (i.e., target) at Syria (n = 6300).
To explore the impact of outwardly directed Syrian events, the data were
filtered again to include events that were both directed at (i.e., target)
or directed by (i.e., source) Syria (n = 7990).

>>>>

The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter
streaming API, servers at the University of Texas at Austin collected
the tweets. The servers were run on a stable (LTS) version of Ubuntu
Linus (v. 10.04) and were connected directly to the high-bandwidth UT network
maintained by IT services.

Tweets collected contained one or more of the following keywords:
“syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These
keywords were chosen based on the most distinctive terms used in news
articles covering the Arab Spring in Syria at the time. A node.js script
was used to reinitialize the connection to Twitter's servers whenever the
script timed out due to a period of silence. The script requested data from
the API endpoint using basic HTTP authentication (OAuth was optional, at
the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored
the data directly to the local hard disk. The tweets were then post-processed
with a Python script to convert the JSON-formatted tweets to tab-separated
files, which were then compressed to maximize storage efficiency.

@@

### Event Data
Event data were obtained from the 2012 Integrated Crisis Early Warning
System [ICEWS; @DVN/28075_2015]. The event data were first filtered to
remove incomplete and incorrectly formatted data. They were then filtered
to include only events that were directed at (i.e., `target`) Syria ($n = 6300$).
To explore the impact of outwardly directed Syrian events, the data were
filtered again to include events that were both directed at (i.e., `target`)
or directed by (i.e., `source`) Syria ($n = 7990$).
